### 2021-02-16 Chapter-1/Chapter-1.tex
update

Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different item in the array.

\section{Defense}

Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage site for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.

>>>>

Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.

\section{Defense}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage sites for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.
